### 2017-04-28 paper/jfp-submission/evaluation.tex
tweak

\paragraph{Evaluation Goals}
%
There are four questions we seek to answer with our evaluation:
%
\begin{enumerate}
\item \emphbf{Witness Coverage}
      How many ill-typed programs can we find witnesses for?
\item \emphbf{Witness Complexity}
      How \emph{complex} are the traces produced by the witnesses?
\item \emphbf{Witness Utility}
      How \emph{helpful} %(qualitatively and quantitatively)
      are the witnesses and traces in debugging type errors?
\item \emphbf{Witness-based Blame}
      Can witnesses be used to \emph{locate} the source
      of a type error?
\end{enumerate}

>>>>

\paragraph{Evaluation Goals}
%
There are four questions we seek to answer with our evaluation:
%
\begin{enumerate}
\item \emphbf{Witness Coverage} (\S~\ref{sec:eval:witness-coverage},~\ref{sec:how-safe})
      How many ill-typed programs \emph{admit} witnesses?
\item \emphbf{Witness Complexity} (\S~\ref{sec:trace-complexity})
      How \emph{complex} are the traces produced by the witnesses?
\item \emphbf{Witness Utility} (\S~\ref{sec:advantage-traces},~\ref{sec:user-study})
      How \emph{helpful} %(qualitatively and quantitatively)
      are the witnesses in debugging type errors?
\item \emphbf{Witness-based Blame} (\S~\ref{sec:locating})
      Can witnesses be used to \emph{locate} the source
      of an error?
\end{enumerate}
